### 2022-09-16 main/chapter_searches.tex
add note and ref for claimed good coverage

Nonetheless, this procedure often simulates reasonable-looking test statistic
distributions without relying on the asymptotic approximations.
Toy simulation is an alternative approximation, and in given circumstances
may be better or worse.
Pick your poison.

>>>>

Nonetheless, this procedure often simulates reasonable-looking test statistic
distributions without relying on the asymptotic approximations, and purportedly
with ``good coverage properties''~\cite{
cern2011procedure,
Cranmer2006Statistical
}.
Toy simulation is an alternative approximation, and in given circumstances
may be better or worse.
Pick your poison.
